#  Data Resampling

Load all packages needed to begin resampling.

```{r library3}

library(tidyverse)
library(magrittr)
library(dplyr)
library(purrr)
library(lubridate)
library(amt)
library(elevatr)
library(sf)
library(sp)

```

Next we will read the processed data in for one individual and inspect data

```{r data}

lion <- readRDS("C:/Users/jaran/Desktop/USU_Thesis_Project/Cleaned_Data/ProcessedData/California/Dop6/M280.rds")

head(lion)

```

Now we will transform the processed data into a track to begin our resampling process. 


```{r trk}

trk <- lion %>% mk_track(.x = utme, 
                         .y = utmn, 
                         .t = localtime, 
                         id = collarid,
                         crs = "+proj=utm +zone=10 +datum=WGS84 +units=m +no_defs",
                         all_cols = TRUE)


```


Next we will use `track resample` to convert our localtime to down sample to 4 hour points with 10 minute tolerance. 

```{r resample}

trk %<>% track_resample(rate = hours(4), tolerance = minutes(10)) %>% 
  time_of_day(include.crepuscule = TRUE)

```

Last we will check to see if the data was resampled propoerly then extract the data out of the track and into a new object.


```{r organize}

head(trk)

lion <- trk %>% dplyr::select(no, collarid, latitude, longitude, localtime = t_, utme = x_, utmn = y_, dop, fixtype)

head(lion)

```

Export data into a new folder to organize different resampled data. 

```{r export}

M280 <- saveRDS(lion, "C:/Users/jaran/Desktop/USU_Thesis_Project/Cleaned_Data/ProcessedData/ResampledData/California/4hrs/M280.rds")
M280 <- write.csv(lion, file="C:/Users/jaran/Desktop/USU_Thesis_Project/Cleaned_Data/ProcessedData/ResampledData/California/4hrs/M280.csv", row.names = FALSE)


```


