#  Cluster Identifiation

Load all packages needed to begin and source material. This code was created by Peter Mahoney and can be found at https://github.com/PMahoney29/rAnimalSiteFidelity 

```{r library4}

library(bcpa)
library(rgdal)
library(rgeos)
library(maptools)
library(foreach)
library(doParallel)
library(lubridate)
library(ggplot2)
library(dplyr)
library(raster)

source("rASF.R")

```

Next we will read the resampled data in for one individual and convert the localtime to a specific format of mdy_hm. Next I removed duplicates from the data. 

```{r data3}

d <- read.csv("C:/Users/jaran/Desktop/USU_Thesis_Project/Cleaned_Data/ProcessedData/ResampledData/California/4hrs/M280.csv")
d$dt <- ymd_hms(d$localtime, tz = 'GMT')
d <- d[!duplicated(d$dt),]
coordinates(d) <- d[, c('longitude', 'latitude')]
proj4string(d) <- CRS('+proj=longlat +datum=WGS84')


```

Now we will be sure to project for accurate measurements and note the zone of which the collared individual was collared.


```{r}

utmProj = CRS("+proj=utm +zone=10 +datum=WGS84")
d <- spTransform(d, utmProj)
str(d)


```


Now running a function from the pulled github package to assign all data in a specific order.

```{r}

clustxy <- ClusterXY(xy = coordinates(d), dt = d$dt, 
                     proj4string = utmProj, id = '31756', 
                     PointID = 'no', Data = d@data)

```

Next we assign the parameters to the cluster identifier. nfixes is the total number of points in the location to be considered a cluster. sbuffer is the radius around the cluster that points can be found in. tbuffer is the amount of time that has to past without a new point at the cluster for the cluster to end. intime, inPar, and nCores allow for smoother running of the identifier code. 

```{r}

nfixes = 4
sbuffer = 150
tbuffer = 24
intime = T

inPar = TRUE
nCores = detectCores() - 1

```

Run code below to identify clusters with parameters above.

```{r}

M280_clusters <- visualize_clusters(clustxy, nfixes, sbuffer, tbuffer, intime,
                                    inPar = inPar, nCores = nCores)

summary(M280_clusters)

```

Below I created a for loop to extract all the points in each cluster that was identified but leave the first and last one out. THis will allow me to have a starting and or end point for running an iSSA.


```{r}

temp <- M280_clusters@Data[[1]]
first <- nrow(temp)
last <- 1
toremove <- temp[-c(first,last),]

# Forloop for rest of the dataset

for (i in 2:length(M280_clusters@Data)){
  temp <- M280_clusters@Data[[i]]
  first <- nrow(temp)
  last <- 1
  tempnew <- temp[-c(first,last),]
  toremove <- rbind(toremove, tempnew)
}

```

Lastly export all points that are provided from the for loop above. 

```{r}

M280 <- saveRDS(toremove, "C:/Users/jaran/Desktop/USU_Thesis_Project/Cleaned_Data/ProcessedData/ClustersforRemoval/M280ClusterRemoval.rds")
M280 <- write.csv(toremove, file="C:/Users/jaran/Desktop/USU_Thesis_Project/Cleaned_Data/ProcessedData/ClustersforRemoval/M280ClusterRemoval.csv", row.names = F)

```




