#  Data Resampling

Load all packages needed to remove clusters.

```{r, eval==FALSE}

library(dplyr)
library(magrittr)


```

Next we will read the ressampled data and the cluster identified data in for one individual and inspect data

```{r, eval=FALSE}

ProssData <- read.csv("C:/Users/jaran/Desktop/USU_Thesis_Project/Cleaned_Data/ProcessedData/ResampledData/California/4hrs/M280.csv")

RemoveClust <- read.csv("C:/Users/jaran/Desktop/USU_Thesis_Project/Cleaned_Data/ProcessedData/ClustersforRemoval/California/M280ClusterRemoval.csv")

```

Next we will select PointID in the RemoveClust and change it to no so that both files have an identical column. 


```{r, eval=FALSE}

RemoveClust <- RemoveClust %>% dplyr::select(no = "PointID")

```


Lastly, we will `anti_join the ProssData and RemoveClust by the no column to remove all cluster points from our data.

```{r, eval=FALSE}

CleanedData <- anti_join(ProssData, RemoveClust, by = "no")
```

Finally export all data into a new folder called cleaned data and begin your analysis!!!!

```{r}

M280 <- saveRDS(CleanedData, "C:/Users/jaran/Desktop/USU_Thesis_Project/Cleaned_Data/CleanedData/California/Dop6/M2804hrCleaned.rds")
M280 <- write.csv(CleanedData, file="C:/Users/jaran/Desktop/USU_Thesis_Project/Cleaned_Data/CleanedData/California/Dop6/M2804hrCleaned.csv", row.names = F)


```




